### 2020-07-09 msr.tex
Katy's second review edits

\glspl{MSR} are one of six advanced reactor designs shortlisted by
the Generation IV Forum in 2001 for promising significant advances in safety,
sustainability, efficiency, and cost over existing designs. This
has attracted significant attention and resources towards
\gls{MSR} research, most noticeable by the number of start-up companies that
have emerged in recent years touting various \gls{MSR} designs. This chapter
provides a brief history of \glspl{MSR}, followed by the distinctive features
that earned the concept the label of being a Generation IV reactor. Lastly,
this chapter presents the reference specifications of the \gls{MSFR} concept
studied in this work.

\section{History}

The first \gls{MSR}, named the \gls{ARE}, dates back to the 1940s
as part of the US Aircraft Nuclear Propulsion program
\cite{rosenthal_molten-salt_1970}. Researchers recommended the molten fluoride
salts in particular for high uranium solubility, chemical stability, low vapor
pressure even at high temperatures, decent heat transfer properties,
resistance against radiation damage, and reduced corrosive effects on some
common structural material \cite{rosenthal_molten-salt_1970}. They
subsequently built the 2.5 MW$_{\text{th}}$ ARE reactor at \gls{ORNL}, where
it achieved criticality on November 1954 and generated 100 MWh over nine days.
The fuel consisted of enriched uranium in a molten salt mixture of NaF,
ZrF$_4$, and UF$_4$. Additionally, the reactor used blocks of BeO for neutron
moderation. The aircraft program
ultimately never came to fruition as the development of intercontinental
ballistic missiles effectively eliminated the need for long-range
nuclear-powered bomber aircraft.

@@

\section{Features}

@@

In the past two decades, researchers have developed several
new tools for simulating steady-state and transient behavior in \glspl{MSR}.
Many of the earlier efforts featured simplifications in simulating
thermal-hydraulics by solving 1-D Navier-Stokes equations or using
predetermined uniform velocity fields \cite{krepel_dyn3d-msr_2007,
kophazi_development_2009}. In more recent years, there has been
significant progress towards fully coupled, spatial codes that feature
2-D axisymmetric or full 3-D models. In 2011, Cammi et al.
\cite{cammi_multi-physics_2011} performed a ``\gls{MPM}'' analysis
of a simplified 2-D axisymmetric model of a single \gls{MSBR} fuel channel
using the commercial finite element analysis software COMSOL Multiphysics. The
physics were implemented through the two-group neutron diffusion equations,
and the \gls{RANS} standard $k$-$\epsilon$ turbulence model, for the
neutronics and thermal-hydraulics respectively. The
authors emphasized the need for proper full coupling of the multiphysics and
presented both steady-state and transient results in various
scenarios such as reactivity insertions, changes in pumping rate, and the
presence of periodic perturbations. This approach was featured again in a
later paper by Fiorina et al. \cite{fiorina_modelling_2014} in 2014 for a 2-D
axisymmetric model of the
\gls{MSFR}. The authors presented results from the Politecnico di Milano
COMSOL-based approach, and another approach by researchers from Delft
University of Technology, in which they coupled their in-house neutronics and
thermal-hydraulics codes, DALTON and HEAT respectively. With multigroup
neutron diffusion and \gls{RANS} formulations on ultra fine meshes, both
models agreed on the steady-state neutron flux, temperature,
and \gls{DNP} distributions, as well as the power responses following various
accident transient initiations. Aufiero et al. \cite{aufiero_development_2014}
concurrently developed
a full-core 3-D model of the \gls{MSFR} on OpenFOAM, albeit with one-group
neutron diffusion to reduce computational load. With the 3-D model, the
authors could simulate the asymmetric reactor response to the failure of a
single pump in the sixteen-pump \gls{MSFR} configuration. The authors also
provided quantitative data supporting the use of implicit coupling over
explicit coupling to obtain accurate solutions of the transient cases.
Recognizing the huge computational burden required for full 3-D simulations, 
later authors came up with innovative ways to alleviate this issue. Methods
include
selective geometrical reduced order modeling for various components of a
reactor based on the importance of the physical phenomena being simulated
\cite{zanetti_geometric_2015}, or using a novel, efficient method for
neutronics calculations \cite{laureau_transient_2017}.

@@

The \gls{MSFR} is a European reference fast-spectrum \gls{MSR} concept
\cite{mathieu_thorium_2006, merle_optimized_2007}. Table \ref{table:msfr} and
Figure \ref{fig:msfr} show the main specifications and schematic view of the
\gls{MSFR}, respectively. Developed from the \gls{MSBR} design, the
\gls{MSFR} is intended to run primarily on a closed thorium fuel cycle with
continuous online fuel reprocessing. Several reasons motivated the omission of
graphite moderators from the original \gls{MSBR} design. Graphite is
susceptible to
long-term radiation damage and replacement is likely to be necessary during
the operating lifetime of the reactor. Graphite also has a positive
temperature coefficient of reactivity; eliminating graphite from the design
ensures a greater safety margin \cite{mathieu_thorium_2006}. While negative
temperature coefficients are attainable with very thermalized spectra,
breeding ratios deteriorated significantly due to parasitic absorption in the
graphite \cite{mathieu_thorium_2006}.
%
\begin{figure}[htb!] 
	\centering
	\includegraphics[width=0.8\textwidth]{MSFR}
	\caption{Schematic view of the MSFR concept. Figure reproduced from
	Brovchenko et al. \cite{brovchenko_design-related_2013}.}
	\label{fig:msfr}
\end{figure}
%
\begin{table}[htb!]
    \small
	\caption{Main specifications of the \gls{MSFR} concept
				\cite{serp_molten_2014}.}
	\centering
	\begin{tabular}{ l r }
		\toprule
		Parameter & Value \\
		\midrule
		Thermal/Electric output [MW$_{\text{th}}$/MW$_{\text{e}}$] & 3000 /
		1500 
		\\
		Salt volume [m$^3$] & 18 \\
		Salt fraction in core & 0.5 \\
		Number of circulation loops & 16 \\
		Nominal flow rate [kg s$^{-1}$] & 18500  \\
		Nominal circulation time [s] & 4.0 \\
		Inlet/outlet temperature [K] & 923 / 1023 \\
		Blanket volume [m$^3$] & 7.3\\
		\bottomrule
	\end{tabular}
	\label{table:msfr}
\end{table}

In the \gls{MSFR} design, fuel salt flows vertically upward through a 9 m$^3$
central core region. At the top of the core, the flow separates into sixteen
smaller external loops, each of which passes through a heat exchanger before
being pumped back into the bottom of the core. The salt also passes through
the online salt reprocessing and gas sparging systems located along the
external loops. A toroidal blanket tank containing fertile salt for breeding
surrounds the core radially. The top and bottom of the core are enclosed
by nickel alloy reflectors. A layer of boron carbide behind the blanket tanks
protects the peripheral equipment from excessive neutron damage. During severe
accidents when core temperatures rise to dangerous levels, the actively
fan-cooled freeze plug at the bottom of the core melts and drains the fuel
salt into a containment vessel designed to keep the salt subcritical.

Although the \gls{MSFR} is primarily designed to operate on the thorium fuel
cycle, it supports a range of start-up fuel and feed compositions. This
versatility is particularly important for the first few \glspl{MSFR} to be
deployed due to the lack of $^{233}$U reserves required for the initial core
loading. In general, the fuel and blanket salts are approximately composed of
eutectic mixtures of 77.5\% LiF - 22.5\% AcF$_4$; AcF$_4$ represents
actinide fluorides such as uranium, thorium, plutonium, and other \gls{TRU}
fluorides. For an initial composition consisting of $^{232}$Th and $^{233}$U,
the benchmark value for the amount of $^{233}$U for criticality under
normal operating conditions is 2.5 mol\%. However, a neutronic benchmark
study by Brovchenko et al. \cite{brovchenko_neutronic_2019} shows that
different neutronics software with different nuclear data clearly provide
different $k_{eff}$ estimates even with the same isotopic compositions and
temperature distributions. The individual co-authors adjusted the
ratio of $^{232}$Th to $^{233}$U slightly to achieve exact criticality at a
uniform temperature of 973 K for their own neutronics software
\cite{brovchenko_neutronic_2019}. This thesis
performs the same exercise to adjust the inlet and outlet temperatures to
match nominal values.

The thermal and electric power output of the \gls{MSFR} are 3000 MW
$_{\text{th}}$ and 1500 MW$_{\text{e}}$, respectively. The high thermal
efficiency ($\eta_{th}=0.5$) is due to the high operating
temperature. The inlet and outlet temperature
specifications of the fuel salt are 923 K and 1023 K, respectively, for a
minimum 50 K temperature buffer between the
operating temperatures and the melting point of the salt (873 K)
\cite{euratom_final_2015}. The \gls{MSFR} has
heat exchangers and an intermediate coolant loop to isolate the power
conversion system from the highly radioactive fuel salt. This also serves as
a layer of containment between the radioactive material and the outside
environment. The exact composition of the intermediate coolant is not
finalized yet but potential candidates include NaF-NaBF$_4$, FLiNaK,
LiF-ZrF$_4$, and FliBe \cite{merle_concept_2017}.

@@

This present work uses the same 2-D square-cylindrical \gls{MSFR} design to
benchmark our results against results published by Fiorina et al.
\cite{fiorina_modelling_2014}. The design is a 2-D axisymmetric representation
of the \gls{MSFR} with the sixteen individual external loops homogenized into
a single outer loop as shown in Figure \ref{fig:msfrgeom}. For the multigroup
group constants calculations in Serpent, the 2-D axisymmetric model is
extended into a 3-D model by a 360-degrees rotation about the
central axis. The material definitions are the same as those specified in the
reference \gls{MSFR} model. Accordingly, the pump and heat exchanger regions
are assumed to be composed of 100\% fuel salt. While this may not be entirely
accurate, the exact details of the pump and heat exchanger systems are still
under active study, and this external loop region is presumed to be of little
neutronic importance due to its position behind the strong boron carbide
neutron absorber layer.
%
\begin{figure}[t!] 
	\centering
	\includegraphics[width=0.5\textwidth]{msfr-geom}
	\caption{2-D axisymmetric model of the \gls{MSFR} core used for the
	simulations in Serpent. All dimensions are in meters.
	\cite{brovchenko_neutronic_2019}}
	\label{fig:msfrgeom}
\end{figure}

Although this present work uses the same 2-D axisymmetric geometry for
generating
group constant data from Serpent, there are two minor differences between the
\gls{MSFR} geometry used in the Moltres model, and the Polimi and TUDelft
models \cite{fiorina_modelling_2014}. Firstly, the reactor geometry for
Moltres excludes the 2-cm-thick structural material around the blanket tank
that separates the fuel and blanket salts. The thickness is much smaller than
the rest of the regions in the geometry and caused issues for meshing. The
neutronics results in Chapter \ref{chap:nts} shows that the overall $k_{eff}$
and other parameters from Moltres show good agreement with that from Serpent.
It also has no direct impact on the temperature distribution results because
this present work solves for the temperature distribution in the primary loop
with homogeneous Neumann boundary conditions on the fuel salt-to-wall
interface. This approach is for consistency with the Polimi and TUDelft
models.

@@

The reference start-up salt composition for the fuel and blanket salts is
77.5\% LiF - 22.5\% AcF$_4$ (actinide fluorides)
\cite{merle-lucotte_launching_2011}. Typically, researchers working with the
\gls{MSFR}
model tweak the exact actinide composition by varying the $^{232}$Th to
$^{233}$U ratio to obtain a $k_{\text{eff}}$ value of 1 at a uniform
temperature of 973 K \cite{brovchenko_neutronic_2019}. Thus, the exact
actinide compositions vary depending on
the nuclear data library and neutron transport code. This present work uses
a fuel salt composition of 77.5\% LiF - 19.913\% ThF$_4$ - 2.587\%
$^{233}$UF$_4$ for all calculations, which is a simplifying assumption but a
fuel burnup analysis is complex and out of scope for this thesis. Table
\ref{table:prip} shows relevant physical properties of the fuel and blanket
salts.
%
\begin{table}[htb!]
\small
\centering
\caption{Properties of the fuel and blanket salts LiF-AcF$_4$.}
\begin{tabular}{l l r r}
\toprule
Property & Formula & {Value at 973 K} & Validity Range\\
\midrule
Melting temperature [K] & 841 & {N/A} & 1 bar \\
Boiling temperature [K] & 1874 & {N/A} & 1 bar \\
Density, $\rho$ [kg m$^{-3}$] & $4094-0.882 \cdot (T-1008)$ & $4125$ & 893-1123 K \\
Dynamic viscosity, $\mu$ [Pa s] & $\rho \cdot 5.55 \times 10^{-8} \cdot e^{3689/T}$ & $1.015$ & 898-1121 K \\
Thermal conductivity, $k$ [W m$^{-1}$ K$^{-1}$] & $0.928+8.397 \times 10^{-5} \cdot T$ & $0.01010$ & 891-1020 K \\
Specific heat, $c_p$ [J kg$^{-1}$ K$^{-1}$] & $-1111+2.78\cdot T$ & $1594$ & 867-907 K \\
\bottomrule
\end{tabular}
\label{table:prip}
\end{table}

@@

The reflectors on the periphery of the reactor core and the blanket tank are
made of a NiCrW Hastelloy (metal alloy) \cite{brovchenko_neutronic_2019}.
Table \ref{table:refl} details the elemental composition
of the Hastelloy. The alloy has a density
of 10 g$\cdot$cm$^{-3}$. The \gls{MSFR} also includes a 20 cm
layer of boron carbide (B$_4$C) to protect the heat exchangers and pumps from
neutron irradiation. The reference specifications indicate that natural boron
is used, which is composed of 19.8 \% $^{10}$B and 80.2 \% $^{11}$B, with an
overall density of 2.52 g$\cdot$cm$^{-3}$. 
%
\begin{table}[htb!]
\footnotesize
\centering
\caption{Composition (mol \%) of the NiCrW Hastelloy.}
\begin{tabular}{l l l l l l l l l l l l l}
\toprule
Ni & W & Cr & Mo & Fe & Ti & C & Mn & Si & Al & B & P & S \\
\midrule
79.432 & 9.976 & 8.014 & 0.736 & 0.632 & 0.295 & 0.294 & 0.257 & 0.252 & 0.052 & 0.033 & 0.023 & 0.004 \\
\bottomrule
\end{tabular}
\label{table:refl}
\end{table}

>>>>

\glspl{MSR} are one of six advanced reactor designs shortlisted by
the Generation IV Forum in 2001 for promising significant advances in safety,
sustainability, efficiency, and cost over existing designs. This
has attracted significant attention and resources towards
\gls{MSR} research, most noticeable by the number of start-up companies that
have emerged in recent years touting various \gls{MSR} designs. This chapter
provides a brief history of \glspl{MSR}, followed by the distinctive features
that earned the concept the label of being a Generation IV reactor. Lastly,
this chapter presents the reference specifications of the \gls{MSFR} concept
studied in this work and summarizes the state of the art in the international
literature regarding modeling and simulation of the \gls{MSFR}.

\section{\gls{MSR} History}

The first \gls{MSR}, named the \gls{ARE}, dates back to the 1940s
as part of the US Aircraft Nuclear Propulsion program
\cite{rosenthal_molten-salt_1970}. Researchers recommended molten fluoride
salts in particular for high uranium solubility, chemical stability, low vapor
pressure even at high temperatures, good heat transfer properties,
resistance against radiation damage, and reduced corrosive effects on some
common structural material \cite{rosenthal_molten-salt_1970}. They
subsequently built the 2.5 MW$_{\text{th}}$ ARE reactor at \gls{ORNL}, where
it achieved criticality on November 1954 and generated 100 MWh over nine days.
The fuel consisted of enriched uranium in a molten salt mixture of NaF,
ZrF$_4$, and UF$_4$. Additionally, the reactor used blocks of BeO for neutron
moderation. The aircraft program
ultimately never came to fruition as the development of intercontinental
ballistic missiles effectively eliminated the need for long-range
nuclear-powered bomber aircraft.

@@

\section{\gls{MSR} Features}

@@

In the past two decades, researchers have developed several
new tools for simulating steady-state and transient behavior in \glspl{MSR}.
Many earlier efforts featured simplifications in simulating
thermal-hydraulics by solving 1-D Navier-Stokes equations or using
predetermined uniform velocity fields \cite{krepel_dyn3d-msr_2007,
kophazi_development_2009}. In more recent years, there has been
significant progress towards fully coupled, spatial codes that feature
2-D axisymmetric or full 3-D models. In 2011, Cammi et al.
\cite{cammi_multi-physics_2011} performed a ``\gls{MPM}'' analysis
of a simplified 2-D axisymmetric model of a single \gls{MSBR} fuel channel
using the commercial finite element analysis software COMSOL Multiphysics. The
physics were implemented through the two-group neutron diffusion equations,
and the \gls{RANS} standard $k$-$\epsilon$ turbulence model, for the
neutronics and thermal-hydraulics respectively. The
authors emphasized the need for proper full coupling of the multiphysics and
presented both steady-state and transient results in various
scenarios such as reactivity insertions, changes in pumping rate, and the
presence of periodic perturbations. This approach was featured again in a
later paper by Fiorina et al. \cite{fiorina_modelling_2014} in 2014 for a 2-D
axisymmetric model of the
\gls{MSFR}. The authors presented results from the Politecnico di Milano
COMSOL-based approach, and another approach by researchers from Delft
University of Technology, in which they coupled their in-house neutronics and
thermal-hydraulics codes, DALTON and HEAT respectively. With multigroup
neutron diffusion and \gls{RANS} formulations on ultra fine meshes, both
models agreed on the steady-state neutron flux, temperature,
and \gls{DNP} distributions, as well as the power responses following various
accident transient initiations. Aufiero et al. \cite{aufiero_development_2014}
concurrently developed
a full-core 3-D model of the \gls{MSFR} in OpenFOAM, albeit with one-group
neutron diffusion to reduce computational load. With the 3-D model, the
authors could simulate the asymmetric reactor response to the failure of a
single pump in the sixteen-pump \gls{MSFR} configuration. The authors also
provided quantitative data supporting the use of implicit coupling over
explicit coupling to obtain accurate solutions of the transient cases.
Recognizing the huge computational burden required for full 3-D simulations, 
later authors came up with innovative ways to alleviate this issue. Methods
include
selective geometrical reduced order modeling for various components of a
reactor based on the importance of the physical phenomena being simulated
\cite{zanetti_geometric_2015}, or using a novel, efficient method for
neutronics calculations \cite{laureau_transient_2017}.

@@

The \gls{MSFR} is a European reference fast-spectrum \gls{MSR} concept
\cite{mathieu_thorium_2006, merle_optimized_2007}. Table \ref{table:msfr} and
Figure \ref{fig:msfr} show the main specifications and schematic view of the
\gls{MSFR}, respectively. Developed from the \gls{MSBR} design, the
\gls{MSFR} is intended to run primarily on a closed thorium fuel cycle with
continuous online fuel reprocessing. Several reasons motivated the omission of
graphite moderators from the original \gls{MSBR} design. Firstly, graphite is
susceptible to
long-term radiation damage and replacement is likely to be necessary during
the operating lifetime of the reactor. Secondly, graphite also has a positive
temperature coefficient of reactivity; eliminating graphite from the design
ensures a greater safety margin \cite{mathieu_thorium_2006}. Lastly, while
negative temperature coefficients are attainable with very thermalized
spectra, breeding ratios deteriorated significantly due to parasitic
absorption in the graphite \cite{mathieu_thorium_2006}.
%
\begin{figure}[htb!] 
	\centering
	\includegraphics[width=0.8\textwidth]{MSFR}
	\caption{Schematic view of the MSFR concept. Figure reproduced from
	Brovchenko et al. \cite{brovchenko_design-related_2013}.}
	\label{fig:msfr}
\end{figure}
%
\begin{table}[htb!]
    \small
	\caption{Main specifications of the \gls{MSFR} concept
				\cite{serp_molten_2014}.}
	\centering
	\begin{tabular}{ l r }
		\toprule
		Parameter & Value \\
		\midrule
		Thermal/Electric output [MW$_{\text{th}}$/MW$_{\text{e}}$] & 3000 /
		1300 
		\\
		Salt volume [m$^3$] & 18 \\
		Salt fraction in core & 0.5 \\
		Number of circulation loops & 16 \\
		Nominal flow rate [kg s$^{-1}$] & 18500  \\
		Nominal circulation time [s] & 4.0 \\
		Inlet/outlet temperature [K] & 923 / 1023 \\
		Blanket volume [m$^3$] & 7.3\\
		\bottomrule
	\end{tabular}
	\label{table:msfr}
\end{table}

In the \gls{MSFR} design, fuel salt flows vertically upward through a 9 m$^3$
central core region. At the top of the core, the flow separates into sixteen
smaller external loops, each of which passes through a heat exchanger before
being pumped back into the bottom of the core. The salt also passes through
the online salt reprocessing and gas sparging systems located along the
external loops. A toroidal blanket tank containing fertile salt for breeding
surrounds the core radially. The top and bottom of the core are enclosed
by nickel alloy reflectors. A layer of boron carbide behind the blanket tank
protects the peripheral equipment from excessive neutron damage. During severe
accidents when core temperatures rise to dangerous levels, the actively
fan-cooled freeze plug at the bottom of the core melts and drains the fuel
salt into a containment vessel designed to keep the salt subcritical.

Although the \gls{MSFR} is primarily designed to operate on the thorium fuel
cycle, it supports a range of start-up fuel and feed compositions. This
versatility is particularly important for the first few \glspl{MSFR} to be
deployed due to the lack of $^{233}$U reserves required for the initial core
loading. In general, the fuel and blanket salts are approximately composed of
eutectic mixtures of 77.5\% LiF - 22.5\% AcF$_4$; AcF$_4$ represents
actinide fluorides such as uranium, thorium, plutonium, and other \gls{TRU}
fluorides.  For an initial composition consisting of $^{232}$Th and $^{233}$U,
the benchmark value for the amount of $^{233}$U for criticality under
normal operating conditions is 2.5 mol\%. However, a neutronic benchmark
study by Brovchenko et al. \cite{brovchenko_neutronic_2019} shows that
different neutronics software with different nuclear data provide
different $k_{eff}$ estimates even with the same isotopic compositions and
temperature distributions. The individual co-authors adjusted the
ratio of $^{232}$Th to $^{233}$U slightly to achieve exact criticality at a
uniform temperature of 973 K for their own neutronics software
\cite{brovchenko_neutronic_2019}. This thesis
performs the same exercise to adjust the inlet and outlet temperatures to
match nominal values.

The thermal and electric power output of the \gls{MSFR} are 3000 MW
$_{\text{th}}$ and 1300 MW$_{\text{e}}$, respectively. The high thermal
efficiency ($\eta_{th}=0.43$) is due to the high operating
temperature. The inlet and outlet temperature
specifications of the fuel salt are 923 K and 1023 K, respectively, for a
minimum 50 K temperature buffer between the
operating temperatures and the melting point of the salt (873 K)
\cite{euratom_final_2015}. The \gls{MSFR} has heat exchangers and an
intermediate molten salt coolant loop to separate the power
conversion system from the highly radioactive fuel salt. This also serves as
a layer of containment between the radioactive material and the outside
environment. The exact composition of the intermediate coolant is not
finalized yet but potential candidates include NaF-NaBF$_4$, FLiNaK,
LiF-ZrF$_4$, and FliBe \cite{merle_concept_2017}.

@@

The present work uses the same 2-D square-cylindrical \gls{MSFR} design to
compare our results to results published by Fiorina et al.
\cite{fiorina_modelling_2014}. The design is a 2-D axisymmetric representation
of the \gls{MSFR} with the sixteen individual external loops homogenized into
a single outer loop as shown in Figure \ref{fig:msfrgeom}. For the multigroup
group constants calculations in Serpent, the 2-D axisymmetric model is
extended into a 3-D model by a 360-degree rotation about the
central axis. The material definitions are the same as those specified in the
reference \gls{MSFR} model \cite{brovchenko_neutronic_2019}. Accordingly, the
pump and heat exchanger regions
are assumed to be composed of 100\% fuel salt. While this is an approximation,
the outer loop is shielded from the core by a layer of boron carbide and sees
sufficiently low neutron fluxes that we may neglect its exact neutronics.
%
\begin{figure}[t!] 
	\centering
	\includegraphics[width=0.5\textwidth]{msfr-geom}
	\caption{2-D axisymmetric model of the \gls{MSFR} core used for the
	simulations in Serpent. All dimensions are in meters.
	\cite{brovchenko_neutronic_2019}}
	\label{fig:msfrgeom}
\end{figure}

Although the present work uses the same 2-D axisymmetric geometry for
generating group constant data from Serpent, there are two minor differences
between the \gls{MSFR} geometry modeled herein, and the geometry used in the
Polimi and TUDelft models \cite{fiorina_modelling_2014}. First, the reactor
geometry for
Moltres excludes the 2-cm-thick structural material around the blanket tank
that separates the fuel and blanket salts. The thickness is much smaller than
the rest of the regions in the geometry and it complicated mesh generation in
the adjacent regions near the boundaries. The
neutronics results in Chapter \ref{chap:nts} show that the overall $k_{eff}$
and other parameters from Moltres show good agreement with that from Serpent.
It also has no direct impact on the temperature distribution results because
the present work solves for the temperature distribution in the primary loop
with homogeneous Neumann boundary conditions on the fuel salt-to-wall
interface. This approach is for consistency with the Polimi and TUDelft
models.

@@

The reference start-up salt composition for the fuel and blanket salts is
77.5\% LiF - 22.5\% AcF$_4$ (actinide fluorides)
\cite{merle-lucotte_launching_2011}. Some researchers working with the
\gls{MSFR} model tweak the exact actinide composition by varying the
$^{232}$Th to $^{233}$U ratio to obtain a $k_{\text{eff}}$ value of 1 at a
uniform temperature of 973 K \cite{brovchenko_neutronic_2019} or for other
unmentioned reasons \cite{fiorina_molten_2013}. Thus, the exact
actinide compositions vary depending on the nuclear data library, neutron
transport code, and the purpose of the study. The present work uses
a fuel salt composition of 77.5\% LiF - 19.913\% ThF$_4$ - 2.587\%
$^{233}$UF$_4$ for all calculations, which gives steady-state inlet and outlet
temperatures approximately equal to the nominal values in Table
\ref{table:msfr}. Table \ref{table:prip} shows relevant physical properties of
the fuel and blanket salts.
%
\begin{table}[htb!]
\small
\centering
\caption{Properties of the fuel and blanket salts LiF-AcF$_4$
\cite{brovchenko_neutronic_2019}.}
\begin{tabular}{l l r r}
\toprule
Property & Formula & {Value at 973 K} & Validity Range\\
\midrule
Melting temperature [K] & 841 & {N/A} & 1 bar \\
Density, $\rho$ [kg m$^{-3}$] & $4094-0.882 \cdot (T-1008)$ & $4125$ & 893-1123 K \\
Dynamic viscosity, $\mu$ [Pa s] & $\rho \cdot 5.55 \times 10^{-8} \cdot e^{3689/T}$ & $1.015$ & 898-1121 K \\
Thermal conductivity, $k$ [W m$^{-1}$ K$^{-1}$] & $0.928+8.397 \times 10^{-5} \cdot T$ & $0.01010$ & 891-1020 K \\
Specific heat, $c_p$ [J kg$^{-1}$ K$^{-1}$] & $-1111+2.78\cdot T$ & $1594$ & 867-907 K \\
\bottomrule
\end{tabular}
\label{table:prip}
\end{table}

@@

The reflectors on the periphery of the reactor core and the blanket tank are
made of a NiCrW Hastelloy (metal alloy) \cite{brovchenko_neutronic_2019}, and
Table \ref{table:refl} details its elemental composition. This alloy has a
density of 10 g$\cdot$cm$^{-3}$. The \gls{MSFR} also includes a 20 cm
layer of boron carbide (B$_4$C) to protect the heat exchangers and pumps from
neutron irradiation. The reference specifications indicate that natural boron
is used, which is composed of 19.8 \% $^{10}$B and 80.2 \% $^{11}$B, with an
overall density of 2.52 g$\cdot$cm$^{-3}$. 
%
\begin{table}[htb!]
\footnotesize
\centering
\caption{Composition (mol \%) of the NiCrW Hastelloy.}
\begin{tabular}{l l l l l l l l l l l l l}
\toprule
Ni & W & Cr & Mo & Fe & Ti & C & Mn & Si & Al & B & P & S \\
\midrule
79.432 & 9.976 & 8.014 & 0.736 & 0.632 & 0.295 & 0.294 & 0.257 & 0.252 & 0.052 & 0.033 & 0.023 & 0.004 \\
\bottomrule
\end{tabular}
\label{table:refl}
\end{table}
